---
title: "Week 6- Graphing Assignment"
author: "Amanda Mae Woodward"
date: "10/18/2021"
output: html_document
---
1. Open the starwars dataset from tidyverse
```{r}
library(tidyverse)
data(starwars)
View(starwars)
```

2.Create a graph of character's eye color. (Hint: pay attention to the class of data)
```{r}
library(Rmisc)
library(ggplot2)
starwars$eyecolor<- as.factor(starwars$eye_color)
eyeColorgraph<- cbind.data.frame(starwars$eye_color)
ggplot(eyeColorgraph, aes(eye_color))+geom_bar()
View(eyecolorGraph)
View(starwars)
                                                    
```


3. Customize your graph to make it more presentable (consider axes, colors, themes)
```{r}
ggplot(eyecolorGraph, aes(eye_color))+geom_bar(color="gold",fill="maroon")
 ```

4. Create a graph of character's height versus mass.
```{r}
ggplot(starwars, aes(mass, height))+geom_point()

```

5. Customize this graph to make it more presentable.
```{r}
ggplot(starwars, aes(mass, height))+geom_point(color="blue")+xlab(label = "Character Mass") +ylab(label= "Character Height")
```

6. Create another graph of character's height and mass. Include sex as a third variable.  
```{r}
ggplot(starwars, aes(mass, height, color=sex)) +geom_point()
```

7. Customize this graph to make it more presentable. 
```{r}
ggplot(starwars, aes(mass, height, color=sex))+geom_point()+xlab(label = "Character Mass(In Kg)") +ylab(label= "Character Height (In inches)")
```

