title: "PSY4960 Graphing Assignment"
author: "Amanda Mae Woodward"
date: "10/28/2021"
output: html_document
---
1. Open the starwars dataset (located in tidyverse)
```{r}
library(tidyverse)
data(starwars)
```

2. Create a scatter plot of character's height and mass. 
```{r}
library(ggplot2)
ggplot(starwars, aes(height, mass))+geom_point()
```


2a. Change the color and shape of the points in your scatter plot. 
```{r}
ggplot(starwars, aes(height, mass))+geom_point(color="gold", fill="green")
```


3. Add Homeworld as a third variable to your scatterplot. 
```{r}
ggplot(starwars, aes(height, mass, color= homeworld))+geom_point()
```


3a. What do you notice about the graph? (e.g. describe what you see)
There is a fat outliar. I think his name is jabba

4. Make a boxplot of height. 
```{r}
ggplot(starwars, aes (height, mass, color=homeworld))+ geom_boxplot()
```


5. Make a boxplot of height for each species present in the data. 

5a. change the appearance of your graph. 

6. Using any variables in the starwars dataset, create a graph that uses a color pallette from viridis.
```{r}
colnames(starwars)
library(viridis)
ggplot(starwars, aes(height, mass))+geom_point()+scale_fill_viridis(option="magma")
```


7.6. Using any variables in the starwars dataset, create a graph that uses a color pallette from RColorBrewer.
```{r}
ggplot(starwars, aes(height, mass))+geom_point()+scale_color_brewer(palette+"GnBu")
```

