1.Open the sleep dataset in R 
```{r}
data(sleep)
```
2. Is it long or wide format? How do you know? 
```{r}
View(sleep)
```
3. Transform this data so it is in the other format
```{r}
colnames(sleep)
wideSleep<- pivot_wider(sleep, id_cols = "ID") names_from="group", values_from="extra")
```


4. Transform your data back to its original format. 
```{r}
View(sleep)
sleepLonger<- pivot_longer(sleep, cols = c("ID", "group")), names_to("Participant information"), values_to("extra")
```

5. Open the Starwars dataset
```{r}
library(dplyr)

data(starwars)
View(starwars)
```

6. Create homeworld as a factor. How many levels does it have?
```{r}
world<- as.factor(starwars$homeworld)
levels(world)
```

7. Reorder homeworld so that Naboo is the reference group. 
```{r}
relevel(world,ref = "Naboo")
```

8. Use mutate to create a column transforming kg to pounds. (hint: you may need to look up the conversion)
```{r}
starwars$weight<-starwars%>%
  mutate(weight = mass * 2.205)%>%
  select(mass, weight)
```

9. Print a summary of your column from #8
```{r}
summary(starwars$weight)
```

