---
title: "Quiz 1"
author: "Woodward"
date: "10/6/2021"
output: html_document
---
---
title: 'PSYC4960: Quiz 1'
author: "Amanda Mae Woodward"
date: "10/17/2020"
output: html_document
---
Assignment: For this assignment, you will need to use the skills you have developed in the last two weeks. You **are** allowed to work with each other

**Pt 1**
1. Create a dataframe containing two columns: one with five super heroes, and one with your rating of how effective they are (1 = not effective; 10 = very effective)
```{r}
superheroes <- c("Wonderwoman", "Aquaman", "Captain Hindsight", "Spiderman", "Batman")
efficacy <- c(10, 4, 1, 6, 5)
superheroEfficacy <- cbind.data.frame(superheroes,efficacy)
```

2. What are the mean and standard deviation of your ratings?
```{r}
mean(efficacy)
sd(efficacy)
```

3. Print just the row containing your highest ranked hero.
```{r}
superheroEfficacy[1,]
```

4. Write a logical statement to determine if your highest ranked superhero and second highest ranked hero have the same ranking
```{r}
superheroEfficacy[1,] == superheroEfficacy[4,]
```


**Part 2**
5. Create a function that indicates whether a number is above 50 or 50 or under
```{r}
fiftyMark <- function(number){
  if (number > 50) {print("Greater than 50")}
  if (number < 50) {print("Less than 50")}
  if (number == 50) {print("Equal to 50")}
}
```

6. Test your function by inputting the number 19
```{r}
fiftyMark(19)
```

7. Create a vector containing the numbers 1 through 100.
```{r}
vector <- seq(1:100)
```
8. Modify your function to test whether all numbers in a vector are even or odd. (hint: this means you need to iterate through a list!)
###I was trying to use is.integer to test if the iterations through the vector are divisible by 2 and still an integer to test if they're even but I can't figure out how to make it work####
```{r}
for (i in vector) {
  evenIhope <- i %% 2
  if (evenIhope == 0) {print("even")}
  if (evenIhope == 1) {print("odd")}
}
```

9. Test your new function using the vector in #6. 
```{r}

}

```

**Pt 3**
All questions will use the diamonds dataset (in the ggplot2 library).

10. Summarize the dataset.
```{r}
library(ggplot2)
data(diamonds)
summary(diamonds)
```

11. What type of variable is cut? How do you know? 
```{r}
class(diamonds$cut)
```

12. What type of variable is price? How do you know?
```{r}
class(diamonds$price)
```


13. Create a subset of the dataset that contains all diamonds with a VS1 clarity. 
```{r}
subset(diamonds, diamonds$clarity=="VS1")
```

14.How many diamonds are in this dataset?
```{r}
length(diamonds$clarity=="VS1")
```

15. Add a column to this subset indicating whether a diamonds' carat is small (less than the first quartile), average (between the first and third quartile), or large (greater than the third quartile).
```{r}
quant <- quantile(diamonds$carat, probs = c(.25, .5, .75))
diamonds$size <- NA
for (i in 1:length(diamonds$carat)){
  if(diamonds$carat[i]<quant[[1]]){diamonds$size[i]<- "small"}
  if (diamonds$carat[i]>quant[[1]] & diamonds$carat[i]<quant[[3]]){diamonds$size[i]<- "average"}
  if (diamonds$carat[i]>quant[[3]]){diamonds$size[i]<- "large"}
c}
```


