title: "PSY4960-Week 4 Assignment"
author: "Amanda Mae Woodward"
date: "9/22/2021"
output: html_document
---
1.create a vector of 8 tv show names.
```{r}
tvShows <- c("new girl", "twin peaks", "30 rock","stranger things", "seinfeld", "downton abbey","arrested development","criminal minds")
```

2. What kind of data is this? explain how you know.
This kind of data is character type, you can check the kind of data by using class(x):
```{r}
class(tvShows)
```

3. Change your vector to a factor. 
```{r}
as.factor(tvShows)
```

4. Create a function that multiplies numbers by 13. 
```{r}
timesThirteen <- function(number)(number*13)
timesThirteen(2)
```

5. Create a dataframe that consists of one vector, which  contains the numbers 1-13
```{r}
thirteen <- seq(1:13)
throughThirteen <- cbind.data.frame(thirteen)
```

6. Test your function from #4 by creating a new column in your dataframe from #5 that contains the output from your function for the numbers 1-13  (i.e. use the column you already made to test your function)
```{r}
throughThirteen$output <- NA
throughThirteen$output <- timesThirteen(thirteen)
View(throughThirteen)
```

7. Use a for loop to determine if the numbers in your column from #6 are even or odd. *Challenge* save this output to another column in your data frame. 
```{r}
for (i in 1:length(throughThirteen$output)){
  Numbers <- i%%2
  if (Numbers ==0) {print("even")}
  if (Numbers ==1) {print("odd")}
}
```

8. use if/else statements to create a column that indicates whether the numbers in the column created for #6 are "bigger" than 100 or "smaller" than 100. 
```{r}

throughThirteen$greaterOrlesser<-NA
throughThirteen$greaterOrlesser<- for (i in 1:nrow(throughThirteen)){
  if (i < 100) {throughThirteen$greaterOrlesser[i] == "smaller"}
  if (i > 100) {throughThirteen$greaterOrlesser[i] == "bigger"}
  if (i == 100) {throughThirteen$greaterOrlesser[i] == "equal to"}

}
```

